\textbf{EECS 340: Assignment 2}

### 2020-02-04 assignment_2/article.tex
🐛 Correct Problem 2 conclusion.
🔨 Update Problem 2 justifications i.c.w. the corrected conclusion.

\paragraph{Answer}

\begin{gather}
    \frac{1}{n^a} \ll \frac{1}{n^\epsilon} \ll \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \\
    \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)} \ll (\log n)^a \ll n^{\epsilon} \\
    \ll a^{\log_a(n)} \equiv \epsilon n \equiv \frac{n}{a} \ll n^a \equiv (n+b)^a\\
    \ll (n+a)^b \ll n^{a+b} \ll \epsilon^n \ll a^{\epsilon n} \equiv a^n \ll b^n
\end{gather}

\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b)$\newline}

@@

\begin{gather}
    \log(n^\epsilon) = \epsilon \log(n) \\
    \log(n^a) = a \log(n) \\
    \log(bn) = \log(b) + \log(n) \\
    \log(n^b) = b \log(n)
\end{gather}

@@

\paragraph{Justification of $ \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $0 < \epsilon < \frac{1}{2}$)} \equiv \log(n^b) \leq \log_{\frac{1}{\epsilon}}(n) \text{ \ (when $\epsilon \geq \frac{1}{2}$)}$\newline}

It is known that when $\epsilon < \frac{1}{2} \Rightarrow \frac{1}{\epsilon} \geq 2$; when $\epsilon \geq \frac{1}{2} \Rightarrow  \frac{1}{\epsilon} \leq 2$. Since it is observable that $\log_{x}(n) \gg \log_{x'}(n)$ for $x < x'$, such (in)equaility is valid.

@@

The above equations can be rewrite as:
\begin{gather}
    a^{\log_a(n)} = n^1 = \Theta(n) \\
    \epsilon n = \Theta(n) \\
    frac{n}{a} = \frac{1}{a}n =  \Theta(n)
\end{gather}

@@

\paragraph{Justification of $a^{\epsilon n} \equiv a^n$\newline}

We may rewrite $a^{\epsilon n}$ as the following, since there must be a $c$ for $c \in \mathbb{R^+}$ which satisfy the equality.

\begin{gather}
    a^{\epsilon} \cdot a^n = c \cdot a^n = \Theta(a^n)
\end{gather}

Since it is known that $a^n = \Theta(a^n)$, these two expressions are considered equivalent.

>>>>

\subsection{Conclusion}

\begin{gather}
     n^{-a} \ll n^{-\epsilon} \ll \epsilon^n  \\
    \ll \log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b) \equiv \log_{\frac{1}{\epsilon}}(n)\\
    \ll  (\log n)^a \ll n^{\epsilon} \ll a^{\log_a(n)} \\
    \equiv \epsilon n \equiv \frac{n}{a} \\
    \ll n^a \equiv (n+b)^a \ll (n+a)^b \ll n^{a+b} \\
    \ll a^{\epsilon n} \equiv a^n \ll b^n
\end{gather}

\subsection{Justifications}

\paragraph{Justification of $n^{-a} \ll n^{-\epsilon} \ll \epsilon^n$\newline}

\begin{gather}
    \lim\limits_{n \to \infty} \frac{\epsilon^n}{n^{-\epsilon}} = \lim\limits_{n \to \infty} \frac{n\log \epsilon}{-\epsilon \log n} = \lim\limits_{n \to \infty} \frac{\log \epsilon}{-\epsilon} \cdot \frac{n}{\log n} \\
    \text{Since } \epsilon \in (0, 1) \Rightarrow \log \epsilon < 0 \Rightarrow \frac{\log \epsilon}{\epsilon} > 0 \nonumber\\
    \lim\limits_{n \to \infty} \frac{\epsilon^n}{n^{-\epsilon}} = \lim\limits_{n \to \infty} c \cdot \frac{n}{\log n} = \infty \\
    \Rightarrow \epsilon^n \gg n^{-\epsilon}
\end{gather}

\begin{gather}
    \text{Since } 0 < \epsilon < 1 < a \\
    \lim\limits_{n \to \infty} \frac{n^{-a}}{n^{-\epsilon}} = \lim\limits_{n \to \infty} n^{\epsilon - a} = 0 \\
    \Longrightarrow n^{-a} \ll n^{-\epsilon}
\end{gather}

Combine the above two set of equations together, we have $n^{-a} \ll n^{-\epsilon} \ll \epsilon^n$.

\paragraph{Justification of $\epsilon^n \ll \log(n^\epsilon)$\newline}

Since $\lim\limits_{n \to \infty} \epsilon^n = 0$, where $0 < 1 < \log(n^\epsilon)$, we may say the above inequality if true.

\paragraph{Justification of $\log(n^\epsilon) \equiv \log(bn) \equiv \log(n^a) \equiv \log(n^b) \equiv \log_{\frac{1}{\epsilon}}(n)$\newline}

@@

\begin{gather}
    \log(n^\epsilon) = \epsilon \log(n) \\
    \log(n^a) = a \log(n) \\
    \log(bn) = \log(b) + \log(n) \\
    \log(n^b) = b \log(n) \\
\end{gather}

@@

The relationship of the above expressions with $\log_{\frac{1}{\epsilon}}(n)$ can be a bit unintuitive, we may show they are considered equivalent with:
\begin{gather}
    \lim\limits_{n \to \infty} \frac{\log(n^\epsilon)}{\log_{\frac{1}{\epsilon}}(n)} = \lim\limits_{n \to \infty} \frac{\epsilon \log_{2}n}{\frac{\log_{2}n}{\log_{2}(\frac{1}{\epsilon})}} = \lim\limits_{n \to \infty} \epsilon \log_2(\frac{1}{\epsilon}) = c \nonumber\\
    \Rightarrow \log(n^\epsilon) \equiv \log_{\frac{1}{\epsilon}}(n)
\end{gather}

\paragraph{Justification of $ \log(n)\ll  (\log (n))^a $\newline}
\begin{gather}
    \lim\limits_{n \to \infty} \frac{(\log (n))^a}{\log (n)} = \lim\limits_{n \to \infty} (\log(n))^{a-1} = \infty \nonumber \\
    \Rightarrow  \log(n)\ll  (\log (n))^a
\end{gather}

Considered $ \log(n)$ is a generalized form of the perivous group of functions,  $(\log (n))^a$ is proven to be greater than the perivous group.

\paragraph{Justification of $  (\log n)^a \ll n^{\epsilon} \ll a^{\log_a(n)}$\newline}

\begin{gather}
    \lim\limits_{n \to \infty} \frac{\log((\log(n)^a))}{\log(n^\epsilon)} = \lim\limits_{n \to \infty} \frac{a \cdot \log((\log(n)))}{\epsilon \log(n)} = 0 \nonumber \\
    \Rightarrow (\log n)^a \ll n^{\epsilon}
\end{gather}

And it is apparent to see $n^{\epsilon} \ll  a^{\log_a(n)}$ since $ a^{\log_a(n)} = n$; as $\epsilon \in (0, 1)$, there will always be $n^{\epsilon} \ll n$.

@@

The above equations can be rewrite as:
\begin{gather}
    a^{\log_a(n)} = n^1 = \Theta(n) \\
    \epsilon n = \Theta(n) \\
    \frac{n}{a} = \frac{1}{a}n =  \Theta(n)
\end{gather}

@@

\paragraph{Justification of $n^a \equiv (n+b)^a \ll (n+a)^b \ll n^{a+b}$\newline}

These are all polynomial functions with greatest power $> 1$, thus they are considered greater than the previous group (functions with greatest power $= 1$), and ordered according to ascending of \textit{power(s)}.

\paragraph{Justification of $n^{a+b} \ll a^{\epsilon n} $\newline}

$n^{a+b}$ is considered much greater than $a^{\epsilon n}$ due to its nature of being an exponential function.

\paragraph{Justification of $a^{\epsilon n} \equiv a^n \ll b^n$\newline}

\begin{gather}
    \lim\limits_{n \to \infty} \frac{a^{\epsilon n}}{a^n} = \lim\limits_{n \to \infty} a^{\epsilon} = c \nonumber \\
    \Rightarrow a^{\epsilon n} \equiv a^n
\end{gather}

Also it is apparent to see that $a^n \ll b^n$ due to $1 < a < b$. Thus, the inequality is justified.
